% Question 1
\section*{1. (10 points) Find the derivative of the following functions (No need to simplify):}

(a) $f(x)=\sqrt{x}\cdot \tan(x^{2}+1)$  

(b) $g(t)=\frac{\cos t}{3+2\sin t}$  

\newpage

% Question 2
\section*{2. (10 points) Find the limit using l'Hospital's Rule (where you can apply).}

(a) $\lim_{x\rightarrow0}\frac{e^{x}-1-x}{x^{2}}$  

(b) $\lim_{x \to \infty} \dfrac{\ln x}{x}


\newpage

% Question 3
\section*{3. (10 points) Find the derivative $\frac{dy}{dx}$ (or $y^{\prime}$) by implicit differentiation.}

$xe^{y}=x-y$  

\newpage

% Question 4
\section*{4. (10 points) $f(x)=x^{3}-3x^{2}+5$ }

(a) (7 pts) Find the intervals on which $f$ is increasing or decreasing. 

(b) (3 pts) Find the local maximum and minimum values of $f$ using the First Derivative Test. 

\newpage

% Question 5
\section*{5. (10 points) Find the dimensions of a rectangle with area 400 $m^{2}$ whose perimeter is as small as possible.}

(Hint: Area = length $\cdot$ width, Perimeter $= 2$(length) + $2$(width)) 

\newpage

% Question 6
\section*{6. (10 points) Find the function $f(x)$ using anti-derivatives.}

$f^{\prime\prime\prime}(x)=\sin x,$ $f(0)=2,$ $f^{\prime}(0)=1.$ $f^{\prime\prime}(0)=3$ 

\newpage

% Question 7
\section*{7. (10 points) Find the below integrals.}

(a) Indefinite Integral: $\int\frac{5x^{2}+2+\sqrt{x}}{x}dx$ 

(b) Definite Integral: $\int_{-1}^{3}(e^{x}-\pi)dx$ 

\newpage

% Question 8
\section{8. (10 points)}

 Two cars start moving from the same point. One travels north at $3$ mi/h and the other travels east at $4$ mi/h. At what rate is the distance between the cars increasing one hour later?

(Hint: Pythagorean theorem: $(dist)^{2}=x^{2}+y^{2})$  

\newpage

% Question 9
\section*{9. (10 points)}

(a) (5 pts) Use the Fundamental Theorem of Calculus to find the derivative of the function $f^{\prime}(x)$. 

$f(x) = \int_{0}^{\tan x} t e^{-t^{2}} dt$

(b) (5 pts) If $\int_{1}^{7} f(x) dx = 10$ and $\int_{1}^{7} g(x) dx = 5$, find $\int_{1}^{7} [3f(x) - 2g(x)] dx$.

\newpage

% Question 10
\section*{10. (10 points)} 

$f(x) = 1 + 3x^{2} - 2x^{3}$ 

(a) (5 pts) Find the inflection points of $f$, and the intervals on which $f$ is concave upward or concave downward.

(b) (5 pts) Find the local maximum and minimum values of $f$ using the Second Derivative Test. 

\newpage

% Question 11
\section*{Bonus Problem (Extra 10 points)}

(a) Find the integral by using substitution: $\int x e^{x^{2}} dx$ 

(b) Find the integral: $\int_{-2}^{2} (x^{99} + x^{3} + x) dx$ 

\end{document}