\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{MAC 2312 Calculus II – Exam 1}
\lhead{Fall 2024}
\rfoot{Page \thepage}

\begin{document}

\begin{center}
    \textbf{\Large MAC 2312 CALCULUS II} \\
    \textbf{CRN 83557 – MWF} \\
    \vspace{0.2cm}
    \textbf{\Large Exam 1} \\
    \vspace{0.2cm}
    Term: Fall 2024 \\
    \vspace{0.3cm}
    \textbf{Full Name: \underline{\hspace{8cm}}}
\end{center}

\vspace{0.5cm}

\textbf{Instructions:}
\begin{enumerate}
    \item Total time: 1 hour 15 minutes.
    \item Write the information requested above.
    \item Switch off any electronic devices.
    \item Calculators are not allowed.
    \item Write the solution in the given space.
    \item Show all your work for full credit.
    \item Scratch papers are provided but will not be graded.
\end{enumerate}

\vspace{0.5cm}

\begin{tabular}{|c|c|c|}
    \hline
    \textbf{Q.N.} & \textbf{Points} & \textbf{Score} \\
    \hline
    1 & 10 & \\
    2 & 10 & \\
    3 & 10 & \\
    4 & 10 & \\
    5 & 10 & \\
    6 & 10 & \\
    Bonus & 10 & \\
    \hline
    \textbf{Total} & 60 & \\
    \hline
\end{tabular}

\vspace{1cm}

\begin{enumerate}
    \item[1.] (10 points) Find the area of the region bounded by the curves (integrate with respect to $x$):\\
    \[
    y = x^2 + 2x, \quad y = 4x
    \]

    \item[2.] (10 points) \textbf{(Disk Problem)} Find the volume of the solid obtained by rotating the region bounded by\\
    \[
    y = \sqrt{x + 2}, \quad x = -1, \quad x = 1
    \]
    about the $x$-axis.

    \item[3.] (10 points) Find the integral using \textbf{Integration by Parts}:\\
    \[
    \int_0^{\frac{\pi}{2}} x \sin x \, dx
    \]

    \item[4.] (10 points) Find the integral using \textbf{Trigonometric Substitution}:\\
    \[
    \int \frac{x}{\sqrt{4 - x^2}} \, dx
    \]
    (Hint: Substitute $x = 2\sin\theta$, find $dx$, then integrate.)

    \item[5.] (10 points) Find the integral using \textbf{Partial Fraction Decomposition}:\\
    \[
    \int \frac{1}{x^2 - 3x} \, dx
    \]

    \item[6.] (10 points)
    \begin{itemize}
        \item[(a)] Find the average value of the function on the given interval: $f(x) = 2x - 1$, on $[0, 2]$
        \item[(b)] Find $c$ in the given interval such that $f_{\text{avg}} = f(c)$.
    \end{itemize}

    \item[Bonus.] (Extra 10 points) Find the volume of the solid obtained by rotating the region bounded by\\
    \[
    y = x^2, \quad y = \sqrt{x}
    \]
    about the $y$-axis.
\end{enumerate}

\end{document}
