% Question 1
\section*{1.}
The curve $C$ is described by the position vector $\vec{r}(t) = (\sin t)\hat{\imath} + t\hat{\jmath} + (\cos t)\hat{k}$.

\begin{itemize}
    \item[(a)] (5 points) Find $\vec{T}(t)$, the unit tangent vector.
    \item[(b)] (5 points) Find $\vec{N}(t)$, the unit normal vector.
    \item[(c)] (5 points) Find the tangent line to the space curve at the point when $t = \pi$.
\end{itemize}

\newpage

% Question 2
\section*{2.}
Given points $P(1, 3, -1)$, $Q(-1, 5, 0)$ and $R(4, 0, 2)$, find:

\begin{itemize}
    \item[(a)] (3 points) The vectors $\vec{QP}$ and $\vec{QR}$.
    \item[(b)] (5 points) A vector orthogonal to the plane determined by $P$, $Q$, and $R$.
    \item[(c)] (4 points) The equation of the plane determined by $P$, $Q$, and $R$.
\end{itemize}

% Question 3
\section*{3.}
(10 points) Let $f(x, y) = {6(1 + xy + x^2)}^{1/2$}. Find the linear approximation (i.e., the linearization) of $f$ around the point $(2, 2)$ and use it to find the approximate value of $f(2.1, 1.8)$.

\newpage

% Question 4
\section*{4.}
(12 points) Suppose the acceleration of a hang glider is given by
\[
\vec{a}(t) = -3\cos t \, \hat{\imath} - 3\sin t \, \hat{\jmath} + 2 \hat{k}
\]

\begin{itemize}
    \item[(a)] Find the velocity, given initial velocity $\vec{v}(0) = 2\hat{\imath} + 3\hat{\jmath} + \hat{k}$.
    \item[(b)] Find the position, given initial position $\vec{s}(0) = 3\hat{\jmath}$.
\end{itemize}

\newpage

% Question 5
\section*{5.}
(10 points) Show that the following limit does not exist:
\[
\lim_{(x,y)\to(0,0)} \frac{xy}{x^2 + y^2}
\]

% Question 6
\section*{6.}
(12 points) Determine if the two planes are parallel, perpendicular, or neither. If neither, find the cosine of the angle between the planes:

\[
2x - y + z = 2 \quad \text{and} \quad x + y + z = 3
\]

\newpage

% Question 7
\section*{7.}
\begin{itemize}
    \item[(a)] (10 points) Let $w = f(x, y, z) = x^2y + x\sqrt{1 + z}$ and let the point  $P$ have the coordinates $(1, 2, 3)$. Find the directional derivative of $f(x,y,z)$ at the point $P$ in the direction of $\vec{v} = \langle 2, 1, -2 \rangle$.
    \item[(b)] (3 points) At $P$, in what direction is the maximum rate of change?
\end{itemize}

\newpage

% Question 8
\section*{8.}
\begin{itemize}
    \item[(a)] (5 points) Given $w = w(x, y, z)$, $x = x(s, t)$, $y = y(s, t)$, $z = z(s, t)$, write out the chain rule for $\dfrac{\partial w}{\partial t}$.
    \item[(b)] (5 points) Let $w = x e^y + y\sin z - \cos z$, with $x = 2\sqrt{t}$, $y = st + \ln t$, $z = s + 4t$. Find $\dfrac{\partial w}{\partial t}$ when $t = 1$ and $s = 0$.
\end{itemize}

\newpage

% Question 9
\section*{9.}
(15 points) Find and classify all critical points of:
\[
f(x, y) = x^3 - 3x - y^3 + 12y
\]

\newpage

% Question 10
\section*{10.}
(12 points) Evaluate the double integral:
\[
\int_0^2 \int_{y/2}^1 e^{x^2} \, dx\, dy
\]
\begin{itemize}
    \item[(a)] Sketch the region of integration.
    \item[(b)] Change the order of integration and evaluate.
\end{itemize}

\newpage

% Question 11
\section*{11.}\text
(5 points) Find the Jacobian of the transformation: $x = u + 2v$, $y = 3u + 5v$.

% Question 12
\section*{12.}
(12 points) Using polar coordinates, evaluate:
\[
\iint_D (x + y) \, dA
\]
Where $D$ is the region in the upper half of the $xy$-plane bounded by $x^2 + y^2 = 4$ and $x^2 + y^2 = 16$.

\newpage

% Question 13
\section*{13.}
(12 points) Use a triple integral to find the volume of the tetrahedron in the first octant bounded by the coordinate planes $x = 0$, $y = 0$, $z = 0$, and the plane $x + 2y + z = 2$.

% Question 14
\section*{14.}
(0 points, Bonus) What is a space curve?

